paper1_results_figs_slimmed_50_rr

### 2016-07-04 inst/documents/paper1_results_figs_slimmed_50_rr.Rmd
fig bigger
correct bug in classification tree figures

## Figures for paper 1 : version 7

@@

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, fig.height=3.5}

@@

@@

  #just doing for a few strategies, sensiAnPpaer1All.Rmd does for a bunch
  treeResponses <- c( rownames(resistBetterMix_ASeq)[2], #2 is 25%
                      rownames(resistBetterMix_ASeq20)[2]
                    )

@@

    cpOptimal <- tree$cptable[ tree$cptable[,"rel error"] + tree$cptable[,"xstd"]  < tree$cptable[,"xerror"],"CP"][1]

    treePruned <- prune(tree, cp=cpOptimal)

@@

>>>>

## Figures for paper 1 : version 8

@@

```{r, eval=TRUE, echo=FALSE, warning=FALSE, fig.height=5.5}

@@

```{r, eval=TRUE, echo=FALSE, warning=TRUE, message=FALSE, fig.height=3.5}

@@

  #4/7/16 need to remove runs where gens >= 500
  length(which(resistPointsSeq['gen_cP0.5',] >= 500 | resistPointsMix_A['gen_cP0.5',] >= 500))
  #2376
  length(which(resistPointsSeq['gen_cP0.5',] >= 500 ))
  #2151
  length(which(resistPointsMix_A['gen_cP0.5',] >= 500))
  #2306

  #BEWARE1 of subtracting if diff num in each ...
  #this removes runs that fail either

  failed_run_indices <- (resistPointsSeq['gen_cP0.5',] >= 500 | resistPointsMix_A['gen_cP0.5',] >= 500)

  resistPointsMix_A <- resistPointsMix_A[,!failed_run_indices]
  resistPointsSeq <- resistPointsSeq[,!failed_run_indices]
  #BEWARE2 I need to remove these indices from the predictors too
  treeInput <- treeInput[,!failed_run_indices]

@@

  #just doing for a few strategies, sensiAnPpaer1All.Rmd does for a bunch
  # treeResponses <- c( rownames(resistBetterMix_ASeq)[2], #2 is 25%
  #                     rownames(resistBetterMix_ASeq20)[2]
  #                   )
  #4/7/16 eek above before was a bug showing 25% rather than 50%
  treeResponses <- c( "betterMix_ASeq_cP0.5","betterMix_ASeq20_cP0.5")

@@

    cpOptimal <- tree$cptable[ tree$cptable[,"rel error"] + tree$cptable[,"xstd"]  < tree$cptable[,"xerror"],"CP"][1]
    treePruned <- prune(tree, cp=cpOptimal)

@@

  #4/7/2016 testing the unpruned trees, repeats previous loop with pruning removed
  for( treeResponse in treeResponses )
  {
    tree <- rpart::rpart(as.formula(paste(treeResponse,"~",treePredictorString)), data = treeInput, method = 'class')

    #to set box colours
    cols <- ifelse(tree$frame$yval == 1, "red", "green3")

    #adds in no. scenarios correctly and incorrectly classified
    prp(tree, extra=1, varlen = 0, main=main, box.col=cols, under=TRUE)
  }
